New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?

### 2024-07-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.Rmd
submission weiter

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer,
      papaja)
```

@@

# disruption & confidence rating

df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") |> 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) |> # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
         "confidence_factor",
         "event"
         ) |> 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data

df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") |> # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID

df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") |> 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132")
         )

@@

main <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) |> 
  mutate(time = Time - min(Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) |>
    # filter(time <= 600) |> # filter for 10min intervals
    filter(time <= 7200) |> # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) |>
  bind_rows()

main <-
  left_join(main, df_merge,
            by = "ID")

main <- 
  main %>% 
  dplyr::select("time", "heart_rate", "ID", "time_span") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  dplyr::summarise(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = main,
             by = "ID") %>% 
  filter(!(time_span == "teaching" & time > 600)) %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

@@

N_postwrangling <- as.numeric(length(unique(main$ID)))

@@

descrip_hr_overall <- main |>
  filter(time_span %in% c("overall")) |> 
  summarise(N = n_distinct(ID),
            "M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

@@

descrip_hr_overall_std <- main |>
  filter(time_span %in% c("overall")) |> 
  summarise(N = n_distinct(ID),
            "M std heart rate in bpm" = round(mean(heart_rate_std),
                                              digits = 2),
            "SD std heart rate in bpm" = round(sd(heart_rate_std),
                                               digits = 2),
            "Min std heart rate in bpm" = round(min(heart_rate_std),
                                                digits = 2),
            "Max heart rate in bpm" = round(max(heart_rate_std),
                                            digits = 2)
            )

@@

descrip_hr_phases <- main |> 
  filter(!time_span %in% c("overall")) |> 
  group_by(time_span) |> 
  summarise(N = n_distinct(ID),
            "M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

@@

descrip_hr_phases_std <- main |> 
  filter(!time_span %in% c("overall")) |> 
  group_by(time_span) |> 
  summarise(N = n_distinct(ID),
            "M heart rate in bpm" = round(mean(heart_rate_std),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate_std),
                                      digits = 2),
            "Min heart rate in bpm" = round(min(heart_rate_std),
                                            digits = 2),
            "Max heart rate in bpm" = round(max(heart_rate_std),
                                            digits = 2)
  )

# # format and insert table in manuscript
# descrip_hr_phases |>
# papaja::apa_table(
#   caption = "Mean, SD and range for teachers' heart rate in individual phases",
#   # note = "Write Note here",
#   escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
#   placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
#   font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
#   )

@@

rating_table <- 
  df_rating |> 
  filter(!is.na(confidence_factor),
         !is.na(disruption_factor)) |> 
   summarise(N = n_distinct(ID), 
            "M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confidence factor" = round(mean(confidence_factor),
                                     digits = 2),
            "SD confidence factor" = round(sd(confidence_factor),
                                      digits = 2),
            "Min confidence factor" = min(confidence_factor),
            "Max confidence factor" = max(confidence_factor)
            )
```

@@

descrip_hr_phases_std <-  descrip_hr_phases_std |> 
  rename(`M HR` = `M heart rate in bpm`,
         `SD HR` = `SD heart rate in bpm`,
         `Min` = `Min heart rate in bpm`,
         `Max` = `Max heart rate in bpm`,
         Interval = time_span)

@@

print(tab_1)

@@

```{r loess-plot, include=FALSE}
df_heart_rate <- 
  main |> 
  mutate(time = time / 60) |> 
  filter(time_span == "overall") |>
  dplyr::select("ID","time","heart_rate") |> 
  distinct() |> 
  mutate(type = "a. Heart Rate (in Beats per Minute)")

df_heart_rate_std <- 
  main |> 
  mutate(time = time / 60) |> 
  filter(time_span == "overall") |>
  dplyr::select("ID","time","heart_rate_std") |> 
  distinct() |> 
  transmute(ID,
            time,
            type = "b. Heart Rate (Standardized)",
            heart_rate = heart_rate_std)

df_heart_rate |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.95) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) + 
 labs(x = "",
      y = "",
      ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y") -> loess_hr

df_heart_rate_std |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.95) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0, 0.25)) +
  labs(x = "",
       y = "",
       ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y") -> loess_hr_std

@@

ggsave(loess_comp,
       filename = "plots_publication/loess_plot_std_unstd_new.pdf",
       width = 16,
       height = 12,
       units = "cm")
```

@@

```{r, include=FALSE}

# main |> 
#   filter(time_span != "overall") |>
#   dplyr::select("ID","time_span", "time","heart_rate_std") |> 
#   mutate(time_span = factor(time_span,
#                             levels = c("preparation","teaching","post","interview","end"),
#                             labels = c("(1) Pre-teaching\nInterval","(2) Teaching\nInterval","(3) Post-teaching\nInterval","(4) Interview\nInterval","(5) End\nInterval"))) |> 
#   distinct() |>
#   group_by(time_span) |> 
#   summarise(z_mean = mean(heart_rate_std),
#             z_sd = sd(heart_rate_std),
#             z_t = qt(p = 0.05 / 2,      # 0.01 KI
#                df = n() - 1,
#                lower.tail = F
#                ),
#             z_error = z_sd / sqrt(n()),
#             lower = z_mean - z_t * z_error,
#             upper = z_mean + z_t * z_error,
#             ) |> 
#   ungroup() |> 
#   ggplot(mapping = aes(x = factor(0),
#                        y = z_mean)) + 
#   geom_point() +
#   geom_errorbar(mapping = aes(ymin = lower,
#                               ymax = upper),
#                 width = 0.2) +
#   geom_hline(yintercept = 0,
#              linetype = "dashed") +
#   scale_y_continuous(breaks=seq(-1, 1, 0.5), 
#                      limits=c(-1.1, 1)) + 
#   labs(x = "Time (in Minutes)",
#        y = "Standardized Mean Heart Rate",
#        # caption = expression(paste(italic("Note: "),
#        #                            "The shadow around the line represents the 99% confidence interval."
#        #                            )
#        #                      )
#        ) +
#   facet_grid(cols = vars(time_span),
#              scales = "free_x") +
#   theme_apa() +
#   theme(axis.text.x = element_blank(),
#         axis.ticks.x = element_blank(),
#         plot.caption = element_text(hjust = 0))
# 
# ggsave(filename = "plots_publication/mean_plot.png",
#        width = 20,
#        height = 12,
#        units = "cm")
```

>>>>

library(needs)
needs(ltm,
      broom,
      ppcor,
      jtools,
      lm.beta,
      tidyverse,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      viridis, 
      stargazer,
      papaja,
      grid)
```

@@

# disruption & confidence rating
df_rating <- 
  excel_sheets("data/Coding_SRI.xlsx") |> 
  map_df(~read_xlsx("data/Coding_SRI.xlsx",.)) |>  # read in data with two sheets
  dplyr::select(ID, # select relevant columns 
         "disruption_factor", # -99 = subject did not notice event; -100 = experimenter did not asked for event
         "confidence_factor",
         "event"
         ) |> 
  mutate(disruption_factor = ifelse(disruption_factor < 0,
                                    yes = NA,
                                    no = disruption_factor
                                    ),
         confidence_factor = ifelse(confidence_factor < 0,
                                   yes = NA,
                                   no = confidence_factor),
         event = as_factor(event)
         )

# demographic data
df_demo <- 
  read_excel("./data/data_empschul_labor_lehrperson.xlsx") |>  # read in excel 
  transmute(ID = LI06_05, # select and rename relevant columns 
            gender = factor(LI02_01_1,
                            levels = 1:2,
                            labels = c("male","female")
                            ),
            age = LI03_01, # 1 = male; 2 = female
            teaching_experience = LI04_01)

# merge two data frames by ID 
df_merge <- merge(df_demo,
                  df_rating,
                  by = "ID") |> 
  filter(!ID %in% c("126", # exclude cases with no fitbit data (to check see data Heart Rate)
                    "132",
                    "236")
         )

@@

# single bpm values (data frame with only single measurement point)

main_single_hr <-
map(.x = dir(path = data_path,
             pattern = ".csv"),
    ~ read_csv(file.path(data_path, .), 
               id = "id",
               col_types = c("t","n")
               ) %>% 
  mutate(time = Time - min(Time),
         time = as.numeric(time),
         heart_rate = `Heart Rate`,
         ID = id,
         time_span = case_when(str_detect(string = id, pattern = "_a") ~ "end",
                               str_detect(string = id, pattern = "_m") ~ "teaching",
                               str_detect(string = id, pattern = "_p") ~ "preparation",
                               str_detect(string = id, pattern = "_s") ~ "post",
                               str_detect(string = id, pattern = "_i") ~ "interview",
                               TRUE ~ "overall"
                               ),
         ID = str_extract(string = ID,
                          pattern = "[:digit:]{3}"),
         ID = as.numeric(ID)
      ) |> 
    # filter(time <= 600) |>  # filter for 10min intervals
    filter(time <= 7200) |>  # filter for 2 hours (maximal duration of study)
    dplyr::select(!c("Time","Heart Rate","id"))
    ) |> 
  bind_rows()

# adding z-standardized HR

main_single_hr <-
  main_single_hr |> 
  dplyr::select("time", "heart_rate", "ID", "time_span") |> 
  distinct() |> 
  group_by(ID) |> 
  dplyr::summarise(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) |> 
  ungroup() |> 
  right_join(y = main_single_hr,
             by = "ID") |> 
  filter(!(time_span == "teaching" & time > 600)) |> 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

## count for individuals

main_single_hr |> 
  filter(time >= 7200) |> 
  distinct(ID, .keep_all = TRUE) -> filter_overall

@@

N_postwrangling <- as.numeric(length(unique(main_single_hr$ID)))

@@

descrip_hr_overall <- main_single_hr |> 
  filter(time_span %in% c("overall")) |> 
  summarise(N = n_distinct(ID),
            "M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

@@

descrip_hr_overall_std <- main_single_hr |> 
  filter(time_span %in% c("overall")) |> 
  summarise(N = n_distinct(ID),
            "M std heart rate in bpm" = round(mean(heart_rate_std),
                                              digits = 2),
            "SD std heart rate in bpm" = round(sd(heart_rate_std),
                                               digits = 2),
            "Min std heart rate in bpm" = round(min(heart_rate_std),
                                                digits = 2),
            "Max heart rate in bpm" = round(max(heart_rate_std),
                                            digits = 2)
            )

@@

descrip_hr_phases <- main_single_hr |> 
  filter(!time_span %in% c("overall")) |> 
  group_by(time_span) %>% 
  summarise(N = n_distinct(ID),
            "M heart rate in bpm" = round(mean(heart_rate),
                                     digits = 2),
            "SD heart rate in bpm" = round(sd(heart_rate),
                                      digits = 2),
            "Min heart rate in bpm" = min(heart_rate),
            "Max heart rate in bpm" = max(heart_rate)
  )

@@

descrip_hr_phases_std <- main_single_hr |> 
  filter(!time_span %in% c("overall")) |> 
  group_by(time_span) |> 
  summarise(N = n_distinct(ID),
            "M heart rate std" = round(mean(heart_rate_std),
                                     digits = 2),
            "SD heart rate std" = round(sd(heart_rate_std),
                                      digits = 2),
            "Min heart rate std" = round(min(heart_rate_std),
                                            digits = 2),
            "Max heart rate std" = round(max(heart_rate_std),
                                            digits = 2)
  )

@@

rating_table <- 
  df_rating |> 
  filter(!is.na(confidence_factor),
         !is.na(disruption_factor)) |> 
   summarise(N = n_distinct(ID), 
            "M disruption factor" = round(mean(disruption_factor),
                                     digits = 2),
            "SD disruption factor" = round(sd(disruption_factor),
                                      digits = 2),
            "Min disruption factor" = min(disruption_factor),
            "Max disruption factor" = max(disruption_factor),
            "M confidence factor" = round(mean(confidence_factor),
                                     digits = 2),
            "SD confidence factor" = round(sd(confidence_factor),
                                      digits = 2),
            "Min confidence factor" = min(confidence_factor),
            "Max confidence factor" = max(confidence_factor)
            )

@@

descrip_hr_phases_std <-  descrip_hr_phases_std |> 
  rename(`M HR` = `M heart rate std`,
         `SD HR` = `SD heart rate std`,
         `Min` = `Min heart rate std`,
         `Max` = `Max heart rate std`,
         Interval = time_span)

@@

@@

```{r loess-plot, include=FALSE}
df_heart_rate <- 
  main_single_hr |> 
  mutate(time = time / 60) |> 
  filter(time_span == "overall") |>
  dplyr::select("ID","time","heart_rate") |> 
  distinct() |> 
  mutate(type = "a. Heart Rate (in Beats per Minute)")

df_heart_rate_std <- 
  main_single_hr |> 
  mutate(time = time / 60) |> 
  filter(time_span == "overall") |>
  dplyr::select("ID","time","heart_rate_std") |> 
  distinct() |> 
  transmute(ID,
            time,
            type = "b. Heart Rate (Standardized)",
            heart_rate = heart_rate_std)

df_heart_rate |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.95
              ) +
  scale_color_viridis_d(option = "A",
                        end = 0.8
                        ) +
  scale_linetype_manual(values = c(1, 6)
                        ) +
  scale_x_continuous(expand = c(0.01,0)
                     ) + 
 labs(x = "",
      y = "",
      ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y"
             ) + 
  theme(plot.margin = margin(r = 15,
                             t = 20,
                             b = 20)
        ) -> loess_hr

df_heart_rate_std |> 
  ggplot(mapping = aes(x = time,
                       y = heart_rate
                       )
         ) +
  geom_smooth(se = T,
              size = 0.5,
              colour = "black",
              level = 0.95) +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0.01,0)) +
  scale_y_continuous(expand = c(0, 0.25)) +
  labs(x = "",
       y = "",
       ) +
  theme_apa() + 
  facet_wrap(~ type,
             ncol = 2,
             scales = "free_y"
             ) +
  theme(plot.margin = margin(r = 30,
                             t = 20,
                             b = 20)
        ) -> loess_hr_std

@@

ggsave(loess_comp,
       filename = "plots_publication/loess_plot_std_unstd_new.pdf",
       width = 20,
       height = 15,
       units = "cm")
```

@@

We first tested the hypothesis that teachers showed the highest mean standardized HR during the micro-teaching unit, compared to all other intervals (Hypothesis 1a). Repeated measures ANOVA revealed that the mean standardized HR differed statistically significantly between intervals, F(4, 400) = 260.62, p < .05, f = 1.60 (large effect). Post-hoc contrasts indicated that, as hypothesized, the mean was significantly higher in the teaching interval (I2) than in all other intervals (see also Fig. 4). Specifically, it was higher than in the pre-teaching interval (I1; t(400)  = -10.08, p < .05, d = 1.03; large effect), the post-teaching interval (I3; t(400) = -6.94, p < .05, d = 1.37; large effect), the interview interval (I4; t(400) = 15.00, p < .05, d = 3.29; large effect), and the end interval (I5); t(400) = 22.54, p < .05, d = 4.64; large effect).

```{r}
box_plot <-
  main_single_hr |> 
  filter(time_span != "overall") |>  
  dplyr::select("ID",
         "time_span",
         "heart_rate_std") |> 
  mutate(time_span = fct_recode(time_span,
                                "Pre-teaching Interval" = "preparation",
                                "Teaching Interval" = "teaching",
                                "Post-teaching Interval" = "post",
                                "Interview Interval" = "interview",
                                "End Interval" = "end"
                                ),
         time_span = factor(time_span,
                            levels = c("Pre-teaching Interval",
                                       "Teaching Interval",
                                       "Post-teaching Interval",
                                       "Interview Interval",
                                       "End Interval"
                                       ),
                            labels = c("Pre-Teaching\nInterval",
                                       "Teaching\nInterval",
                                       "Post-Teaching\nInterval",
                                       "Interview\nInterval",
                                       "End\nInterval")
                            )
         ) |> 
  distinct() |> 
  group_by(ID, time_span) |> 
  summarise(mean_hr_std = 
              mean(heart_rate_std, 
                   na.rm = TRUE)
            ) |> 
  ggplot(mapping = aes(x = time_span,
                       y = mean_hr_std
                       )
         ) +
  geom_boxplot()+
  scale_y_continuous(breaks=seq(-2, 2, 1), 
                     limits=c(-2, 2)
                     ) +   
  # geom_jitter(width = 0.2) +
  theme_apa() + 
  theme(axis.text.x = 
          element_text(
            color="black",
            size = 12),
        plot.caption = element_text(hjust = 0)
        ) + 
  labs(x = "",
       y = "Mean Standardized Heart Rate",
       caption = expression(
         paste(italic("Note: N"), 
               "= 81 participants per interval. Fig. shows median (bold line), interquartile range (box) and outliers (dots)."
         )
       ))

ggsave(filename = "plots_publication/box_plot.pdf",
       plot = box_plot,
       width = 20,
       height = 15,
       units = "cm")
```

```{=latex}
\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \caption{Distribution of the standardized heart rate means in the five intervals}
  \label{Distribution of the standardized heart rate means in the five intervals}
\end{figure}
```

Next, we examined HR changes (i.e., mean slopes) within each interval to test for the hypothesis that HR increased during the pre-teaching interval and decreased during all other intervals (Hypothesis 1b). The mean intercepts and mean slopes, complemented by their standard deviations for each interval, are shown in Table 2; the graphical representation of the slopes is displayed in Figure 5. The mean slope of the pre-teaching interval (I1) was significantly positive, indicating an increase in HR, as hypothesized. Further, the mean slopes of the teaching interval (I2) and post-teaching interval (I3) were significantly negative, indicating a decrease in HR. For the last two intervals, the interview interval (I4)  and end interval (I5), the mean slope was negative but did not differ significantly from zero.

```{r}
df_regression <- 
  main_single_hr %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(time = time / 60) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

fix_models <-
  df_regression %>%
  split(.$Phase) %>%
  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
            data = .)) %>%
  map(
    ~ coef(.) %>%
      tibble::as_tibble(.,
                        rownames = "name") %>%
      transmute(
        type = if_else(str_detect(name,
                                  ":"),
                       true = "slope",
                       false = "intercept"),
        id = str_remove_all(name,
                            "[^[:digit:]]"),
        value = value
      ),

  ) %>%
  bind_rows(.id = "Phase") %>%
  pivot_wider(names_from = type,
              values_from = value)

p.values_slope <-
  fix_models %>%
  split(.$Phase) %>%
  map( ~ t.test(x = .$slope,
                mu = 0)$p.value) %>%
  bind_rows(.id = "Phase") %>%
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_slope")

p.values_intercept <-
  fix_models %>%
  split(.$Phase) %>%
  map( ~ t.test(x = .$intercept,
                mu = 0)$p.value) %>%
  bind_rows(.id = "Phase") %>%
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_intercept")

sd_mean <-
  fix_models %>%
  group_by(Phase) %>%
  dplyr::summarise(
    mean_slope = mean(slope),
    sd_slope = sd(slope),
    mean_intercept = mean(intercept),
    sd_intercept = sd(intercept)
  )

table_data <- 
  right_join(x = sd_mean,
             y = p.values_intercept,
             by = "Phase") %>% 
  right_join(x = .,
             y = p.values_slope,
             by = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(mean_intercept, digits = 3),
            `SD(Intercept)` = round(sd_intercept, digits = 3),
            `p-Value (Intercept)` = p.value_intercept,
            `Mean(Slope)` = round(mean_slope, digits = 3), 
            `SD(Slope)` = round(sd_slope,digits = 3),
            `p-Value (Slope)` = p.value_slope, 
            ) %>% 
  arrange(Phase)

### 2024-07-30 02_paper/02_study/01_fitbit paper/Submission/FitBit_submission.tex
submission weiter

>>>>

We first tested the hypothesis that teachers showed the highest mean
standardized HR during the micro-teaching unit, compared to all other
intervals (Hypothesis 1a). Repeated measures ANOVA revealed that the
mean standardized HR differed statistically significantly between
intervals, F(4, 400) = 260.62, p \textless{} .05, f = 1.60 (large
effect). Post-hoc contrasts indicated that, as hypothesized, the mean
was significantly higher in the teaching interval (I2) than in all other
intervals (see also Fig. 4). Specifically, it was higher than in the
pre-teaching interval (I1; t(400) = -10.08, p \textless{} .05, d = 1.03;
large effect), the post-teaching interval (I3; t(400) = -6.94, p
\textless{} .05, d = 1.37; large effect), the interview interval (I4;
t(400) = 15.00, p \textless{} .05, d = 3.29; large effect), and the end
interval (I5); t(400) = 22.54, p \textless{} .05, d = 4.64; large
effect).

\begin{verbatim}
## `summarise()` has grouped output by 'ID'. You can override using the `.groups`
## argument.
\end{verbatim}

\begin{figure}[htbp]
  \centering
  \includegraphics[width=1\textwidth]{plots_publication/box_plot.pdf}
  \caption{Distribution of the standardized heart rate means in the five intervals}
  \label{Distribution of the standardized heart rate means in the five intervals}
\end{figure}
